\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2023-10-23 paper.tex
Remove SI units

\documentclass{article}
\usepackage[letterpaper,top=2cm,bottom=2.5cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage[round]{natbib}
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{geometry}%
\usepackage{color}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{nameref}
\usepackage[right]{lineno}
\usepackage{subcaption}
\usepackage{siunitx}
\usepackage{tikz}
\usetikzlibrary{math,calc,positioning}
\usepackage{url}
\usepackage[symbol]{footmisc}
% JK: turning this off for the moment as I keep clicking through on links
% to the bibliography while reading the text and it's intensely annoying.
% Can reinstate when we're ready to preprint
% \usepackage[hidelinks]{hyperref}

@@

To illustrate the varying levels of information that can be captured in a gARG,
Fig.~\ref{fig-inferred-args} presents graphical representations of genealogies output by two tools that
\emph{do} explicitly infer recombination events, namely \kwarg~\citep{ignatieva2021kwarg} and
\argweaver~\citep{rasmussen2014genome},
and two which do not (\tsinfer\ and \relate).
All inferences are based on the
same underlying dataset from \citet{kreitman1983nucleotide}, a standard benchmark in the classical
ARG literature, for which the minimum number of recombination breakpoints in the absence of recurrent
mutation is 7~\citep{song2003parsimonious}. This dataset comprises 43 biallelic SNPs spanning 2.4Kb of the
\emph{D.~melanogaster} ADH locus on chromosome 2L. Where required for inference purposes we
assume a mutation rate of
% per site per generation may be easier to follow?
\SI{5.49e-9}{per site per generation} and a recombination rate of
\SI{8.4e-9}{per site per generation} \citep{lauterbur2022expanding}, together with
a constant effective population size of 1,000,000.
To focus on the ARG topology rather than estimates of node times, the Y position of each node
is arbitrary, taken from the ranked order of nodes output by each software method.
The version numbers of inference software, the specific inference parameters
needed to reproduce the ARGs, and (where necessary) functions to convert outputs to the
\texttt{tskit} gARG format, are available from our GitHub repository.

>>>>

\documentclass{article}
\usepackage[letterpaper,top=2cm,bottom=2.5cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage[round]{natbib}
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{geometry}%
\usepackage{color}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{nameref}
\usepackage[right]{lineno}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{math,calc,positioning}
\usepackage{url}
\usepackage[symbol]{footmisc}
% JK: turning this off for the moment as I keep clicking through on links
% to the bibliography while reading the text and it's intensely annoying.
% Can reinstate when we're ready to preprint
% \usepackage[hidelinks]{hyperref}

@@

To illustrate the varying levels of information that can be captured in a gARG,
Fig.~\ref{fig-inferred-args} presents graphical representations of genealogies output by two tools that
\emph{do} explicitly infer recombination events, namely \kwarg~\citep{ignatieva2021kwarg} and
\argweaver~\citep{rasmussen2014genome},
and two which do not (\tsinfer\ and \relate).
All inferences are based on the
same underlying dataset from \citet{kreitman1983nucleotide}, a standard benchmark in the classical
ARG literature, for which the minimum number of recombination breakpoints in the absence of recurrent
mutation is 7~\citep{song2003parsimonious}. This dataset comprises 43 biallelic SNPs spanning 2.4Kb of the
\emph{D.~melanogaster} ADH locus on chromosome 2L. Where required for inference purposes we
assume a mutation rate of
$5.49\times10^{-9}$ per site per generation
and a recombination rate of
$8.4\times10^{-9}$ per site per generation
\citep{adrion2020community,lauterbur2022expanding},
together with
a constant effective population size of 1,000,000.
To focus on the ARG topology rather than estimates of node times, the Y position of each node
is arbitrary, taken from the ranked order of nodes output by each software method.
The version numbers of inference software, the specific inference parameters
needed to reproduce the ARGs, and (where necessary) functions to convert outputs to the
\texttt{tskit} gARG format, are available from our GitHub repository.
